### 2024-01-10 pnrs.tex
acm style

%! TeX program = xelatex
%! lang = en-GB
\documentclass[a4paper,11pt]{article}

\usepackage[left=3cm,right=3cm]{geometry}

@@

% DOCUMENT
\begin{document}

% FRONT MATTER
\maketitle
\makeabstract
\acknowledge

@@

\begin{theorem}
    \label{corrected-version:thm}
    The \kl{$\Nat$-rational polynomials} are exactly
    the polynomials in $\CorrectPoly$.
\end{theorem}

\begin{theorem}
    \label{nsf-polynomials:thm}
    In the proof, we actually conclude that
    the \kl{$\Nat$-rational polynomials}
    are exactly those that can be computed 
    by \kl{commutative}
    \emph{star-free} $\Nat$-polyregular functions.
\end{theorem}

>>>>

%! TeX program = xelatex
%! lang = en-GB
\documentclass[sigconf,natbib=false,screen, review,anonymous]{acmart}

@@

\makeabstract
% DOCUMENT
\begin{document}

% FRONT MATTER
\maketitle
\acknowledge

@@

\begin{theorem}
    \label{corrected-version:thm}
    Let $P \in \Rel[\vec{X}]$ be a polynomial.
    The following are equivalent:
    \begin{enumerate}
        \item $P \in \CorrectPoly$,
        \item $P$ is \kl{represented} by a \kl{$\Nat$-rational series},
        \item $P$ is \kl{represented} by a \kl{$\Nat$-polyregular function},
        \item $P$ is \kl{represented} by a \kl{star-free $\Nat$-polyregular function}.
    \end{enumerate}
\end{theorem}
